---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# redshiftr

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

`redshiftr` is an R package designed to help users interact with Amazon Redshift, particularly in situations where direct access to an S3 bucket is not available. This package is a continuation of the original `redshiftTools`, which is no longer actively maintained. While building on the excellent foundation provided by `redshiftTools`, `redshiftr` introduces a few new features and enhancements:

* **Table Creation Without S3 Access:** Unlike the original package, `redshiftr` allows users to create tables in Redshift directly, without the need for an S3 bucket. Please note, however, that this process is considerably slower than the standard method and is recommended only for small tables.

* **Spatial Table Creation (Experimental):** The package also offers the ability to create spatial tables in Redshift, a feature that is currently under active development and is considered highly experimental.

This package is made possible thanks to the original authors of `redshiftTools`, whose work has been extended and improved upon here. Their contributions have laid the groundwork for this ongoing development effort.

## Installation

You can install the latest version of redshiftr directly from GitHub using the following command:

``` r
# Install remotes package if you haven't already
#install.packages("remotes")

# Install redshiftr from GitHub
remotes::install_github("phildonovan/redshiftr")
```

## Example

Below is a simple example demonstrating how to use the `redshift_copy_to()` function to create a table in a Redshift instance. In this example, we'll use the iris dataset and the nc dataset from the sf package.

Before starting, make sure you are connected to your Redshift database using `DBI::dbConnect()`.

```{r example, eval=FALSE}
# Load necessary libraries
library(DBI)
library(redshiftr)
library(sf)

# Connect to your Redshift database (replace with your connection details)
con <- dbConnect(RPostgres::Postgres(),
                 dbname = "your_db_name",
                 host = "your_host",
                 port = 5439,
                 user = "your_username",
                 password = "your_password")

# Example 1: Copying the iris dataset to Redshift
# Create a table in Redshift using the iris dataset
redshift_copy_to(con, df = iris, table_name = "iris_table")

# Example 2: Copying the nc dataset (from sf package) to Redshift
# Load the nc dataset
nc <- st_read(system.file("shape/nc.shp", package = "sf"))

# Create a spatial table in Redshift using the nc dataset
redshift_copy_to(con, df = nc, table_name = "nc_table")

# Disconnect from the database
dbDisconnect(con)
```

